Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-15 writeup/gz_hubble_data.tex
Credit @ckrawczyk for Figure 3. Closes #85.
Cite Land+08 for weighting. Closes #80.

The votes of individual classifiers in GZH were combined to
make a vote fraction for each response ($f_{response}$) to a question in the
classification tree. Votes were weighted \citep[in a method identical to
that described in][]{wil13} such that classifiers who frequently disagreed with
others ended up having very low weights. The weighting $(w)$ was 1
for the top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
classifiers, $w$ was designed to drop smoothly and was effectively zero for the
bottom 1\%.  Since this only affected a tiny percentage of
the classifiers (and an even smaller percentage of the classifications) the
overall effect on the GZH dataset was minimal. The method was effective,
however, at filtering out contributions from random or deliberately
malicious classifiers.

@@

We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in
Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this
analysis was done. We also thank Jennifer Lotz for sharing her $G$-$M_{20}$
measurements for the AEGIS sample.

>>>>

The votes of individual classifiers in GZH were combined to make a vote
fraction for each response ($f_{response}$) to a question in the classification
tree. Votes were weighted in a method similar that in previous versions of
Galaxy~Zoo \citep{lan08,wil13}, such that classifiers who frequently disagreed
with others ended up having very low weights. The weighting $(w)$ was 1 for the
top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
classifiers, $w$ was designed to drop smoothly and was effectively zero for the
bottom 1\%.  Since this only affected a tiny percentage of the classifiers (and
an even smaller percentage of the classifications) the overall effect on the
GZH dataset was minimal. The method was effective, however, at filtering out
contributions from random or deliberately malicious classifiers.

@@

We thank Meg Schwamb and the ASIAA for hosting the ``Citizen Science in
Astronomy'' workshop, 3-7 Mar 2014 in Taipei, Taiwan, at which some of this
analysis was done. We thank Jennifer Lotz for sharing her $G$-$M_{20}$
measurements for the AEGIS sample. We thank Coleman Krawczyk for his assistance
in producing Figure~\ref{fig:decisiontree}.
